---
title: "Data Cleaning for Project 7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(rmarkdown)
```

# 1. LOAD PACKAGES NEEDED

``` {r, message=FALSE}
library(tidyverse)
library(magrittr)
library(sf)
library(stringr)
library(tidycensus)
library(tigris)
library(albersusa)
library(measurements)
library(googlesheets4)
library(haven)
library(readxl)
library(googledrive)
```

# 2. IMPORT US CENSUS DATA

## 2.1 US Census TIGER files

We will import US Census TIGER files using package 'tigris'.

County
```{r, message = FALSE, results = 'hide', warning = FALSE}
county_TIGER <- tigris::counties(cb = TRUE, year = 2018, class = "sf", resolution = '5m') %>%
  dplyr::select(GEOID, STATEFP, ALAND, geometry, NAME) %>%
  dplyr::rename(county.name = NAME) %>%
  dplyr::mutate(ALANDKM2 = ALAND/1000000,
                ALANDMI2 = ALAND*3.8610215854781257*10^(-7),
                FIPS = as.numeric(GEOID)) %>%
  dplyr::select(GEOID, FIPS, county.name, STATEFP, ALAND, ALANDKM2, ALANDMI2, geometry)
```

State: We only need the state name from this dataset.
```{r, message = FALSE, results = 'hide', warning = FALSE}
state_TIGER <- tigris::states(cb = TRUE, year = 2018, class = "sf", resolution = '5m') %>%
dplyr::select(STATEFP,NAME) %>%
dplyr::rename(state.name=NAME) %>%
sf::st_set_geometry(NULL)
```

We merged these two files for final spatial data.
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- county_TIGER %>%
  dplyr::left_join(state_TIGER, by ="STATEFP") %>%
  dplyr::mutate(state.fips.num = as.numeric(STATEFP)) %>%
  dplyr::rename(state.fips = STATEFP) %>%
  dplyr::select(GEOID, FIPS, county.name, state.fips, state.fips.num, state.name, ALAND, ALANDKM2, ALANDMI2, geometry)
```


## 2.2 US Census American Community Survey files

We will import the US Census ACS files using package 'tidycensus'. 

At first, you will need to obtain a census api key at https://api.census.gov/data/key_signup.html. After that, you now register this api key into the system.


```{r, message = FALSE, results = 'hide', warning = FALSE}
tidycensus::census_api_key("YOURCENSUSAPIKEY", overwrite = TRUE, install = TRUE)
```
```{r, include = FALSE}
tidycensus::census_api_key("2f6391f67689e90c017b3034da9580cc7801070f", overwrite = TRUE, install = TRUE)
```


You can identify the variables you need. The data dictionary for ACS 2018 is available at https://api.census.gov/data/2018/acs/acs5/groups.html 

```{r, message = FALSE, results = 'hide', warning = FALSE}
vars.list <- tidycensus::load_variables(2018, "acs5", cache = TRUE)
```


We identified and included the "concept" of the variables of interest
```{r, message = FALSE, results = 'hide', warning = FALSE}
vars.list <- tidycensus::load_variables(2018, "acs5", cache = TRUE) %>%
  dplyr::filter(concept %in% c(
    "UNWEIGHTED SAMPLE COUNT OF THE POPULATION", #	B00001
    "SEX BY AGE", # B01001
    #"RACE", #B02001
    #"HISPANIC OR LATINO ORIGIN BY SPECIFIC ORIGIN",
    "HISPANIC OR LATINO ORIGIN BY RACE", #B03002	
    "EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER", #B15003
    "MEDIAN HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2018 INFLATION-ADJUSTED DOLLARS)", #B19013
    #"POVERTY STATUS IN THE PAST 12 MONTHS BY AGE", 
    "POVERTY STATUS IN THE PAST 12 MONTHS BY SEX BY AGE", #B17001
    #"GINI INDEX OF INCOME INEQUALITY",
    "HEALTH INSURANCE COVERAGE STATUS BY SEX BY AGE", #B27001
    "HOUSEHOLD SIZE BY VEHICLES AVAILABLE", # B08201
    "SEX BY AGE BY DISABILITY STATUS", #B18101
    "UNITS IN STRUCTURE", #B25024
    "TENURE BY OCCUPANTS PER ROOM", #B25014
    "HOUSEHOLDS BY PRESENCE OF PEOPLE UNDER 18 YEARS BY HOUSEHOLD TYPE", #B11005
    "EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER", #B23025
    "GROUP QUARTERS POPULATION", #B26001
    "NATIVITY BY LANGUAGE SPOKEN AT HOME BY ABILITY TO SPEAK ENGLISH FOR THE POPULATION 5 YEARS AND OVER", #B16005
    "LANGUAGE SPOKEN AT HOME BY ABILITY TO SPEAK ENGLISH FOR THE POPULATION 5 YEARS AND OVER"
  ))
```


We extracted ACS data below. This step might take 5-15 minutes to load the data depending on your internet widthband.
```{r, message = FALSE, results = 'hide', warning = FALSE}
ACS_2018 <- tidycensus::get_acs(geography = "county", variables = vars.list$name, year = 2018, geometry = FALSE, tigris_use_cache = FALSE, keep_geo_vars = TRUE, cache = TRUE) 
```

# 3. CREATE FUNCTION FOR LATER USE

Function to calculate percentage
```{r, message = FALSE, results = 'hide', warning = FALSE}
ACS.extract <- function(groupcode){
  test <- ACS_2018 %>%
    dplyr::mutate(calculation = ifelse(variable %in% sumvariable,"sum",ifelse(variable %in% totalvariable,"total",""))) %>%
    dplyr::filter(stringr::str_detect(variable, groupcode)) %>%
    dplyr::group_by(GEOID,calculation) %>%
    dplyr::summarize(estimate = sum(estimate)) %>%
    dplyr::filter(calculation!="") %>%
    tidyr::spread(key=calculation, value=estimate) %>%
    dplyr::mutate(percentage=ifelse(total>0,sum/total*100,NA)) #%>%
    #dplyr::mutate(percentage=sum/total*100) %>%
    #dplyr::select(-2,-3)
  data %<>% 
    dplyr::full_join(test, by="GEOID") %>%
    dplyr::select(-c("sum","total"))
  data
}
```

Function to download from googledrive file to the temp.file
```{r, message = FALSE, results = 'hide', warning = FALSE}
ggdrive.download.temp.file <- function(id){
  temp.file <- tempfile()
  googledrive::drive_download(as_id(id), path = temp.file, overwrite=T)
  temp.file
}
```

Function to read files downloaded from NCCD
```{r, message = FALSE, results = 'hide', warning = FALSE}
read.nccd <- function(id){
  test <- readr::read_csv(ggdrive.download.temp.file(id)) %>%
    dplyr::rename(GEOID = cnty_fips) %>%
    dplyr::select(GEOID, Value) %>%
    dplyr::filter(Value != -1)
  test2 <- data %>% dplyr::full_join(test, by = "GEOID")
  test2
}
```

Function to read BRFSS data
```{r, message = FALSE, results = 'hide', warning = FALSE}
read.brfss <- function(id){
  test <- readr::read_csv(ggdrive.download.temp.file(id)) %>%
    dplyr::filter(Response == "Yes") %>%
    dplyr::rename(state.name = LocationDesc) %>%
    dplyr::select(state.name, Data_Value)
  test2 <- data %>% dplyr::full_join(test, by="state.name")
  test2
}
```


# 4. CLEAN AND CALCULATE COUNTY INDICATORS

demo_population
```{r, message = FALSE, results = 'hide', warning = FALSE}
test <- ACS_2018 %>%
  dplyr::filter(variable=="B00001_001") %>%
  dplyr::select(GEOID,estimate)
data %<>% 
  dplyr::full_join(test, by="GEOID") %>%
  dplyr::rename(demo_population=estimate)
```


demo_landarea
```{r, message = FALSE, results = 'hide', warning = FALSE}
data %<>% dplyr::mutate(demo_landarea = ALANDKM2)
```


demo_popdensity
```{r, message = FALSE, results = 'hide', warning = FALSE}
data %<>% dplyr::mutate(demo_popdensity = demo_population/ALANDKM2)
```


demo_p65more
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B01001_020", "B01001_021", "B01001_022", "B01001_023", "B01001_024", "B01001_025",
                 "B01001_044", "B01001_045", "B01001_046", "B01001_047", "B01001_048", "B01001_049")
totalvariable <- c("B01001_001")
data <- ACS.extract("B01001")
data %<>% dplyr::rename(demo_p65more=percentage)
```


demo_65more
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B01001_020", "B01001_021", "B01001_022", "B01001_023", "B01001_024", "B01001_025",
                 "B01001_044", "B01001_045", "B01001_046", "B01001_047", "B01001_048", "B01001_049")
totalvariable <- c("B01001_001")
test <- ACS_2018 %>%
  dplyr::mutate(calculation = ifelse(variable %in% sumvariable,"sum",ifelse(variable %in% totalvariable,"total",""))) %>%
  dplyr::filter(stringr::str_detect(variable, "B01001")) %>%
  dplyr::group_by(GEOID,calculation) %>%
  dplyr::summarize(estimate = sum(estimate)) %>%
  dplyr::filter(calculation!="") %>%
  tidyr::spread(key=calculation, value=estimate) %>%
  dplyr::rename(demo_65more = sum) %>%
  dplyr::select(GEOID, demo_65more)
data %<>% dplyr::full_join(test, by="GEOID")
```


demo_p60more
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B01001_018", "B01001_019", "B01001_020", "B01001_021", "B01001_022", "B01001_023", "B01001_024", "B01001_025",
                 "B01001_042", "B01001_043", "B01001_044", "B01001_045", "B01001_046", "B01001_047", "B01001_048", "B01001_049")
totalvariable <- c("B01001_001")
data <- ACS.extract("B01001")
data %<>% dplyr::rename(demo_p60more=percentage)
```


demo_60more
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B01001_018", "B01001_019", "B01001_020", "B01001_021", "B01001_022", "B01001_023", "B01001_024", "B01001_025",
                 "B01001_042", "B01001_043", "B01001_044", "B01001_045", "B01001_046", "B01001_047", "B01001_048", "B01001_049")
totalvariable <- c("B01001_001")
test <- ACS_2018 %>%
  dplyr::mutate(calculation = ifelse(variable %in% sumvariable,"sum",ifelse(variable %in% totalvariable,"total",""))) %>%
  dplyr::filter(stringr::str_detect(variable, "B01001")) %>%
  dplyr::group_by(GEOID,calculation) %>%
  dplyr::summarize(estimate = sum(estimate)) %>%
  dplyr::filter(calculation!="") %>%
  tidyr::spread(key=calculation, value=estimate) %>%
  dplyr::rename(demo_60more = sum) %>%
  dplyr::select(GEOID, demo_60more)
data %<>% dplyr::full_join(test, by="GEOID")
```


ses_pnohighschool
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B15003_002", "B15003_003", "B15003_004", "B15003_005", "B15003_006", "B15003_007", "B15003_008", "B15003_009", "B15003_010", "B15003_011", "B15003_012", "B15003_013", "B15003_014", "B15003_015", "B15003_016")
totalvariable <- c("B15003_001")
data <- ACS.extract("B15003")
data %<>% dplyr::rename(ses_pnohighschool=percentage)
```


ses_hhincome
```{r, message = FALSE, results = 'hide', warning = FALSE}
test <- ACS_2018 %>%
  dplyr::filter(variable=="B19013_001") %>%
  dplyr::select(GEOID,estimate)
data %<>% 
  dplyr::full_join(test, by="GEOID") %>%
  dplyr::rename(ses_hhincome=estimate)
```


ses_ppoverty
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B17001_002")
totalvariable <- c("B17001_001")
data <- ACS.extract("B17001")
data %<>% dplyr::rename(ses_ppoverty=percentage)
```


ses_punemployed
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B23025_005")
totalvariable <- c("B23025_001")
data <- ACS.extract("B23025")
data %<>% dplyr::rename(ses_punemployed=percentage)
```


ses_urcode_nchs
```{r, message = FALSE, results = 'hide', warning = FALSE}
test2 <- data.frame(tibble(x = 1:6, y = c("Large central metro", "Large fringe metro", "Medium metro", "Small metro", "Micropolitan", "Noncore"))) %>%
  dplyr::rename(ses_urcode_nchs = y)

tempDir <- tempdir() # unzip to temp folder and temp file
temp.file <- tempfile()
download.file("https://www.cdc.gov/nchs/data/data_acces_files/NCHSURCodes2013.xlsx",temp.file,quiet=TRUE,mode="wb")
test <- readxl::read_excel(temp.file) %>%
  dplyr::rename(FIPS = 'FIPS code',
                x = '2013 code') %>%
  dplyr::left_join(test2,by="x") %>%
  dplyr::select(FIPS, ses_urcode_nchs) %>%
  dplyr::mutate(ses_urcode_nchs = as.factor(ses_urcode_nchs))
data %<>% dplyr::full_join(test, by="FIPS")
```


sv_p17below
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B01001_003", "B01001_004", "B01001_005", "B01001_006",
                 "B01001_027", "B01001_028", "B01001_029", "B01001_030")
totalvariable <- c("B01001_001")
data <- ACS.extract("B01001")
data %<>% dplyr::rename(sv_p17below=percentage)
```


sv_pdisability
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B18101_007", "B18101_010", "B18101_013", "B18101_016", "B18101_019",
                 "B18101_026", "B18101_029", "B18101_032", "B18101_035", "B18101_038")
groupcode <- "B18101"
test <- ACS_2018 %>%
  dplyr::mutate(calculation = case_when(
    variable %in% sumvariable ~ "sum",
    variable == "B18101_001" ~ "B18101_001",
    variable == "B18101_003" ~ "B18101_003",
    variable == "B18101_022" ~ "B18101_022")) %>%
  dplyr::filter(stringr::str_detect(variable, groupcode)) %>%
  dplyr::group_by(GEOID,calculation) %>%
  dplyr::summarize(estimate = sum(estimate)) %>%
  dplyr::filter(calculation!="") %>%
  tidyr::spread(key=calculation, value=estimate) %>%
  dplyr::mutate(sv_pdisability = ifelse((B18101_001 - B18101_003 - B18101_022) > 0, sum / (B18101_001 - B18101_003 - B18101_022) * 100, NA)) %>%
  dplyr::select(GEOID, sv_pdisability)
data %<>% dplyr::full_join(test, by="GEOID")
```


sv_singleparent
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B11005_006", "B11005_007")
totalvariable <- c("B11005_001")
data <- ACS.extract("B11005")
data %<>% dplyr::rename(sv_singleparent=percentage)
```


sv_pminority
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B03002_003")
totalvariable <- c("B03002_001")
data <- ACS.extract("B03002")
data %<>% dplyr::mutate(sv_pminority=100-percentage) %>% dplyr::select(-c(percentage))
```


sv_penglish
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B16005_007", "B16005_008", "B16005_012", "B16005_013", "B16005_017", "B16005_018", "B16005_022", "B16005_023", "B16005_029", 
                 "B16005_030", "B16005_034", "B16005_035", "B16005_039", "B16005_040", "B16005_044", "B16005_045")
totalvariable <- c("B16005_001")
data <- ACS.extract("B16005")
data %<>% dplyr::rename(sv_penglish=percentage)
```


sv_pmultiunit
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B25024_007", "B25024_008", "B25024_009")
totalvariable <- c("B25024_001")
data <- ACS.extract("B25024")
data %<>% dplyr::rename(sv_pmultiunit=percentage)
```


sv_pmobilehome
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B25024_010")
totalvariable <- c("B25024_001")
data <- ACS.extract("B25024")
data %<>% dplyr::rename(sv_pmobilehome=percentage)
```


sv_pcrowding
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B25014_005", "B25014_006", "B25014_007")
totalvariable <- c("B25014_001")
data <- ACS.extract("B25014")
data %<>% dplyr::rename(sv_pcrowding=percentage)
```


sv_pnovehicle
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B08201_002")
totalvariable <- c("B08201_001")
data <- ACS.extract("B08201")
data %<>% dplyr::rename(sv_pnovehicle=percentage)
```


sv_groupquarterpop
```{r, message = FALSE, results = 'hide', warning = FALSE}
test <- ACS_2018 %>%
  dplyr::filter(variable == "B26001_001") %>%
  dplyr::select(GEOID,estimate) %>%
  dplyr::rename(sv_groupquarterpop = estimate)
data %<>% dplyr::full_join(test, by="GEOID")
```


npi_keystone_
```{r, message = FALSE, results = 'hide', warning = FALSE}
test <- readr::read_csv("https://raw.githubusercontent.com/Keystone-Strategy/covid19-intervention-data/master/complete_npis_inherited_policies.csv") %>%
  dplyr::filter(fip_code > 0 & fip_code < 1000) %>%
  dplyr::select(fip_code, npi, start_date) %>%
  dplyr::mutate(npi=str_c("npi_keystone_",npi)) %>%
  tidyr::spread(key=npi, value=start_date) %>%
  dplyr::rename(state.fips.num = fip_code)
data %<>% full_join(test, by="state.fips.num")
```

npi_UW_
```{r, message = FALSE, results = 'hide', warning = FALSE}
test <- readr::read_csv("https://raw.githubusercontent.com/COVID19StatePolicy/SocialDistancing/master/data/USstatesCov19distancingpolicy.csv")
# test <- readr::read_csv("https://raw.githubusercontent.com/cspark2610/SocialDistancing/master/data/USstatesCov19distancingpolicy.csv")
```

npi_CUSP
```{r}
df <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1zu9qEWI8PsOI_i8nI_S29HDGHlIp2lfVMsGxpQ5tvAQ", col_types = "c")
```
?read_sheet

hc_icubeds
hc_icubeds_per1000
hc_icubeds_per60more
hc_hospitals
hc_hospitals_per1000
```{r, message = FALSE, results = 'hide', warning = FALSE}
test <- readr::read_csv(ggdrive.download.temp.file("1t-MG6kM5ZTQOPmZTpVQPnaJvXt6I-z8I")) %>%
  dplyr::rename(GEOID = cnty_fips,
                hc_hospitals = hospitals,
                hc_icubeds = icu_beds) %>%
  dplyr::select(GEOID, hc_hospitals, hc_icubeds)
data %<>% dplyr::full_join(test, by = "GEOID") %>% 
  dplyr::mutate(hc_hospitals_per1000 = hc_hospitals/demo_population*1000,
                hc_icubeds_per1000 = hc_icubeds/demo_population*1000,
                hc_icubeds_per60more1000 = hc_icubeds/demo_60more*1000,
                hc_icubeds_per65more1000 = hc_icubeds/demo_65more*1000)
```


hc_pnotinsured_acs
```{r, message = FALSE, results = 'hide', warning = FALSE}
sumvariable <- c("B27001_004", "B27001_007", "B27001_010", "B27001_013", "B27001_016", "B27001_019", "B27001_022", "B27001_025", "B27001_028",
                 "B27001_032", "B27001_035", "B27001_038", "B27001_041", "B27001_044", "B27001_047", "B27001_050", "B27001_053", "B27001_056")
totalvariable <- c("B27001_001")
data <- ACS.extract("B27001")
data %<>% dplyr::mutate(hc_pnotinsured_acs=100-percentage) %>% dplyr::select(-c(percentage))
```


hc_primarycare
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1F3RtLefhOeahbnwmuCWUzZ2101ugLZtw") %>% dplyr::rename(hc_primarycare = Value)
```


hc_primarycare_per1000
```{r, message = FALSE, results = 'hide', warning = FALSE}
data %<>% dplyr::mutate(hc_primarycare_per1000 = hc_primarycare / demo_population * 1000)
```


como_medicareheartdizprev
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1mLleUl6YqkwedBF7JFoQwEeJBAeoKi7X") %>% dplyr::rename(como_medicareheartdizprev = Value)
```


hc_medicaid
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1A5Y2HWk7ynRNNttNpsEKy13q_XY2ADpH") %>% dplyr::rename(hc_medicaid = Value)
```


como_pdiabetes - Diagnosed Diabetes data
```{r, message = FALSE, results = 'hide', warning = FALSE}
test <- readr::read_csv(ggdrive.download.temp.file("1kmvAdF87LkPWNqwcUkBHAsxg5kghd6L1"), skip=2) %>%
  dplyr::filter(!is.na(State)) %>%
  dplyr::mutate(FIPS = as.numeric(CountyFIPS)) %>%
  dplyr::mutate(como_pdiabetes = as.numeric(Percentage)) %>%
  dplyr::select(FIPS, como_pdiabetes)
data %<>% dplyr::full_join(test, by="FIPS") 
```


como_pobesity - Obesity data
```{r, message = FALSE, results = 'hide', warning = FALSE}
test <- readr::read_csv(ggdrive.download.temp.file("1TaPqepJQl30vShuYgf-eeHEqXnLMj88Z"), skip=2) %>%
  dplyr::filter(!is.na(State)) %>%
  dplyr::mutate(FIPS = as.numeric(CountyFIPS)) %>%
  dplyr::mutate(como_pobesity = as.numeric(Percentage)) %>%
  dplyr::select(FIPS, como_pobesity)
data %<>% dplyr::full_join(test, by="FIPS") 
```


como_htn_hosp
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1SwdQHDSNez1gGSriDVPVCjv2PhGuaR5l") %>% dplyr::rename(como_htn_hosp = Value)
```


como_htn_mort
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1huXZ8LSIQu0XFB_x-VoJgGVt3JrcV3T-") %>% dplyr::rename(como_htn_mort = Value)
```


como_cvd_hosp
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1Q5g58s_ErqpaTePfu8SqsiIUbJWx3dSq") %>% dplyr::rename(como_cvd_hosp = Value)
```


como_cvd_mort
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1X2drlwUOEpyrfwIVAwZ1lV3MeNfv_c6D") %>% dplyr::rename(como_cvd_mort = Value)
```


como_allheartdis_hosp
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1N7GRPHtUSjPpV9GLfjmPqLFttSYQIm94") %>% dplyr::rename(como_allheartdis_hosp = Value)
```


como-allheartdis_mort
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1nAMhVifbQKMKZUmK-AvnW8f_wJrqeBKw") %>% dplyr::rename(allheartdis_mort = Value)
```


como_stroke_hosp
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1_k67F1mJtowjE24dwj4PE8aPbjZ0gsYV") %>% dplyr::rename(como_stroke_hosp = Value)
```


como_stroke_mort
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.nccd("1om-sp4vsBRsf0VesQkTSnA38dPX_O63M") %>% dplyr::rename(como_stroke_mort = Value)
```


como_smoking
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.brfss("14ciNqceww0WnMoVm_HIZs6_UTV8vxeR5") %>% dplyr::rename(como_smoking= Data_Value)
```


como_COPD
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.brfss("1APlfrrVPWogiilNpPZkDTNOcRz0-Wjv9") %>% dplyr::rename(como_COPD= Data_Value)
```


como_asthma
```{r, message = FALSE, results = 'hide', warning = FALSE}
data <- read.brfss("1FXC_Nr1aPo01NxvGjmAUpePjZwXnoJN5") %>% dplyr::rename(como_asthma= Data_Value)
```


como_cancer5yr
```{r, message = FALSE, results = 'hide', warning = FALSE}
test <- readr::read_csv(ggdrive.download.temp.file("12ciyJMjWUirgUCwCwBPwPF_Le2vqtuVb"), skip = 8)
test %<>% 
  dplyr::filter(FIPS!=0) %>% # remove rows with no county values
  dplyr::rename(como_cancer5yr = 4) %>% #rename col
  dplyr::select(FIPS, como_cancer5yr) %>% # select cancer incidence rate variable and fips
  dplyr::mutate(como_cancer5yr = as.character(como_cancer5yr),  # convert to str
                como_cancer5yr = str_remove(como_cancer5yr, "#"),  # remove #
                como_cancer5yr = as.numeric(como_cancer5yr)) %>% # convert to float 
  na.omit() %>%
  arrange(FIPS)
data %<>% dplyr::full_join(test, by="FIPS") 
```


demo_bridgedrace_
```{r, message = FALSE, results = 'hide', warning = FALSE}
url <- paste0("ftp://ftp.cdc.gov/pub/Health_Statistics/NCHS/nvss/bridged_race/pcen_v2018_y1018.sas7bdat.zip") # Paste FTP URL
tempDir <- tempdir() # unzip to temp folder and temp file
temp.file <- tempfile()
download.file(url,temp.file,quiet=TRUE,mode="wb")

df <- haven::read_sas(unzip(file.path(temp.file), exdir = tempDir)) %>%
  rename_all(tolower)
df %<>%
  dplyr::filter(age != 0) %>%
  dplyr::mutate(st_fips = as.character(st_fips),
                co_fips = sprintf("%03d", co_fips),
                fips = paste(st_fips, co_fips, sep=""))

df2 <- df %>%
  select(fips, pop2010_apr, pop2010_jul, pop2011, pop2012,pop2013,pop2014,pop2015,pop2016, pop2017, pop2018) %>% 
  mutate(pop_avg = rowMeans(select(., starts_with('pop'))))
popavg <- df2 %>% select(pop_avg)

df2 <- df %>%
  select(fips, pop2010_apr, pop2010_jul, pop2011, pop2012,pop2013,pop2014,pop2015,pop2016, pop2017, pop2018) %>% 
  mutate(pop_avg = rowMeans(select(., starts_with('pop'))))
popavg <- df2 %>% select(pop_avg)

df3 <- df %>% select(fips, age, hisp, racesex)

df_total <- cbind(df3, popavg)
df_whites <- df_total %>% filter(racesex==1 | racesex == 2 & hisp==1)
df_blacks <- df_total %>% filter(racesex==3 | racesex == 4 & hisp==1)
df_ai <- df_total %>% filter(racesex==5 | racesex == 6 & hisp==1)
df_api <- df_total %>% filter(racesex==7 | racesex == 8 & hisp==1)
df_hisp <- df_total %>% filter(hisp==2)

whites <- df_whites %>% group_by(fips) %>% summarize(whites =sum(pop_avg))
blacks <- df_blacks %>% group_by(fips) %>% summarize(blacks =sum(pop_avg))
american_indians_alaskan <- df_ai %>% group_by(fips) %>% summarise(american_indians_alaskan=sum(pop_avg))
asians_pacific <- df_api %>% group_by(fips) %>% summarise(asians_pacific=sum(pop_avg))
hisp <- df_hisp %>% group_by(fips) %>% summarise(hisp=sum(pop_avg))

df_final <- whites %>% 
  inner_join(blacks, by="fips") %>% 
  inner_join(american_indians_alaskan, by ="fips") %>% 
  inner_join(asians_pacific, by="fips") %>% 
  inner_join(hisp, by="fips")

df_final %<>% 
  mutate(total=whites+blacks+american_indians_alaskan+asians_pacific+hisp) %>% 
  mutate(p_whites=whites/total*100,
         p_blacks=blacks/total*100,
         p_american_indians_alaskan=american_indians_alaskan/total*100,
         p_asians_pacific=asians_pacific/total*100,
         p_hisp= hisp/total*100) %>%
  select(-whites, -blacks, -american_indians_alaskan, -asians_pacific, -hisp) %>% 
  dplyr::rename_all(function(x) paste0("demo_bridgedrace_", x)) %>%
  dplyr::rename(GEOID = demo_bridgedrace_fips)


data %<>% left_join(df_final, by = "GEOID")
```


hc_health_occupation_weighted
```{r, message = FALSE, results = 'hide', warning = FALSE, include = FALSE}
# this code is for an old dataset
# df <- readr::read_csv(ggdrive.download.temp.file("1cQItc9_89QEOHjVnZvf_SGp-4gKxegun")) %>%
#   rename_all(tolower)
# 
# df_final <- df %>% 
#   dplyr::filter(county != 0) %>%
#   dplyr::filter(year == 2015) %>%
#   dplyr::select(county, wtfinl, occ2010) %>% 
#   dplyr::filter((occ2010>= 3000)&(occ2010<=3540)) %>% 
#   dplyr::group_by(county) %>% 
#   stats::aggregate(wtfinl ~ county, ., sum) %>% 
#   dplyr::mutate(wtfinl = wtfinl/12) %>%
#   dplyr::rename(FIPS = county,
#                 hc_health_occupation_weighted = wtfinl)
# 
# 
# summary(df_final$hc_health_occupation_weighted)
# 
# data %<>% left_join(df_final, by = "FIPS")
```

```{r, message = FALSE, results = 'hide', warning = FALSE}
df <- readr::read_csv(ggdrive.download.temp.file("1qy9Y7V8gYcM4qSKF0SFOCBhyPZ0wVMyb"))

df2 <- df %>% 
  select(STATE, STATEA, COUNTY, COUNTYA, 
         FJOAW071, FJOAW072, 
         FJOAW159, FJOAW160,    
         FJOAW247, FJOAW248,
         FJOAW335, FJOAW336,
         FJOAW423, FJOAW424,
         FJOAW599, FJOAW600,
         FJOAW687, FJOAW688,
         FJOAW775, FJOAW776,
         FJOAW863, FJOAW864,
         FJOAW951, FJOAW952,
         FJOAWA39, FJOAWA40) %>% 
  mutate(st_fips = as.character(STATEA),
         co_fips = sprintf("%s", COUNTYA),
         fips = paste(st_fips, co_fips, sep="")) %>% 
  mutate(total = FJOAW071+FJOAW072+ 
           FJOAW159+FJOAW160+ 
           FJOAW247+FJOAW248+
           FJOAW335+FJOAW336+
           FJOAW423+FJOAW424+
           FJOAW599+FJOAW600+
           FJOAW687+FJOAW688+
           FJOAW775+FJOAW776+
           FJOAW863+FJOAW864+
           FJOAW951+FJOAW952+
           FJOAWA39+FJOAWA40) %>% 
  group_by(fips) %>% 
  summarise(healthcare_occ = sum(total))
```

County Health Ranking data
https://www.countyhealthrankings.org/explore-health-rankings/rankings-data-documentation 


```{r}
# Code to read the SAS version dataset
# url <- paste0("https://www.countyhealthrankings.org/sites/default/files/media/document/analytic_data2020.sas7bdat") #2020
url <- paste0("https://www.countyhealthrankings.org/sites/default/files/media/document/analytic_data2019.sas7bdat") #2019
tempDir <- tempdir() # unzip to temp folder and temp file
temp.file <- tempfile()
download.file(url,temp.file,quiet=TRUE,mode="wb")

df <- haven::read_sas(temp.file) %>%
  rename_all(tolower)


```



# 5. THE FINAL CLEAN DATASET

Below is the preview of the firt 30 observations including all county indicators
```{r}
paged_table(data[1:30,], options = list(rows.print = 15))
```

```{r, include = FALSE}
# saveRDS(data, file = "DATA/county_indicators.rds")
```


